PANCHANGE_data_preprocessing

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
reducation of the missingness variable

##Missingness of questionnaire items
#PHQ - baseline
PHQ Missingness NAs per person - count and percentages
```{r PHQ baseline missingness}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    na_per_person_phq_base =         # variable for NA per person
      rowSums(                       
        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the PHQ items at baseline
           %in%
             phq.items_base]
        )
    )
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_base) #have a look at the frequency

dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
  mutate(
    miss_pc_total_phq_base = 
      na_per_person_phq_base/9 # NA per person divided by the amount of items
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_phq_base)
```

>>>>

##Missingness of questionnaire items
#PHQ - baseline
PHQ Missingness NAs per person - count
```{r PHQ baseline missingness}
coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
  mutate(
    na_per_person_phq_base =         # variable for NA per person
      rowSums(                       
        is.na(.[phq.items_base])
        )
    )

coping.glad.phq.raw.id %>%
freq(na_per_person_phq_base, cumul = F) #have a look at the frequency
```
